A Fundamental Measure Theory Functional for Hard-Sphere Contact Densities

### 2012-07-12 papers/contact/paper.tex
some very minor cleanups in contact paper Tested everything on node06.

The first geometry we consider is a number of hard spheres confined
within a spherical cavity.  In
Figures~\ref{fig:sphere-8}-\ref{fig:sphere-16}, we show
the densities and contact densities for several cavity sizes.  In each
case, the number of hard spheres was chosen to set the mean filling
fraction to around 0.3?.  This value was chosen because it roughly
corresponds to the filling fraction of water at standard atmospheric
temperature and pressure in the optimal SAFT model developed by Clark
\emph{et al}\cite{clark2006developing}.

@@

It is also interesting to study a system with opposite curvature.  Put
a (larger) hard sphere in the hard-sphere fluid, and see what the
contact density is around that hard sphere.  This is particularly
relevant when we consider using classical density-functional theory to
model solvation.

@@

\section{Formulas generated from Haskell}

\input{formulas}
\begin{align}
  \Phi_1 &= \phione \\
  \Phi_2 &= \phitwo \\
  \Phi_3 &= \phithree \\
  \frac{d F}{dn_3} &= \dwbdnthree \\
  \frac{d F}{dn_2} &= \dwbdntwo \\
  \frac{d F}{dn_1} &= \dwbdnone \\
  \frac{d F}{d\vec{n}_{2v}} &= \dwbdntwov \\
  \frac{d F}{d\vec{n}_{1v}} &= \dwbdnonev
\end{align}

>>>>

The next geometry we consider is a number of hard spheres confined
within a spherical cavity.  In
Figures~\ref{fig:sphere-8}-\ref{fig:sphere-16}, we show the densities
and contact densities for several cavity sizes \fixme{at a variety of
  filling fractions}.  We chose cavities that are large enough that
the center of the sphere is bulk-like, so that we can interpret the
behavior near the interface as behavior that should be typical of the
behavior of the hard sphere fluid near a concave surface.

@@

It is also interesting to study the hard sphere fluid at a convex
surface.  We did so by placing a (larger) hard sphere in the
hard-sphere fluid, to see how the correlation function behaves near
the surface of that hard sphere.  This is particularly relevant when
we consider using classical density-functional theory to model
solvation.

@@
